Stats

### 2022-03-18 stats/analysis.Rmd
correct col of adult points

```{r vali_data}
vali <- testtrials %>% 
  filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18))
```

@@

```{r variation_hedge_plot}
tmp <- variationHedgeInd

variationHedgeInd <- variationHedgeInd %>% 
  mutate(
    ageInYears = factor(ageInYears, levels = c("3", "4", "5", "18"))
  )

hedge_variation_plot <- ggplot() +
  # child data
  geom_smooth(
    data = variationHedgeInd %>% filter(sample == "kids"),  
    aes(x = ageInYearsExact, y = mean, group = datacollection, lty = datacollection), 
    method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey",
  ) +

  geom_point(
    data = variationHedgeInd %>% filter(sample == "kids"), 
    aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears), shape = datacollection, alpha = datacollection)
  ) +

  geom_pointrange(
    data = variationHedge %>% filter(sample == "kids"), 
    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears), shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
  ) +

  # scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
  scale_shape_manual(values = c(16, 18)) + 
  scale_alpha_discrete(range = c(1, 0.4)) + 
  scale_linetype_manual(values = c("solid", "dashed")) +

  # adult data
  geom_jitter(
    data = variationHedgeInd %>% filter(sample == "adults"), 
    aes(x = 6.5, y = mean, col = as.factor(ageInYears), shape = datacollection), alpha = 0.8, width = .05, height = .01,  
  ) +

@@

  # theme(legend.text = element_text(size = 7),
  #       legend.key.size = unit(0.4, "cm"), 
  #       legend.direction = "vertical", 
  #       legend.position = c(0.89, 0.8), 
  #       legend.spacing.y = unit(0.25, 'cm'))

@@

  geom_point(
    data = variationBoxInd %>% filter(sample == "kids"), 
    aes(x = ageInYearsExact, y = mean, col = as.factor(ageInYears), shape = datacollection, alpha = datacollection)
  ) +

  geom_pointrange(
    data = variationBox %>% filter(sample == "kids"), 
    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(ageInYears), shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
  ) +

  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
  scale_shape_manual(values = c(16, 18)) + 
  scale_alpha_discrete(range = c(1, 0.4)) + 
  scale_linetype_manual(values = c("solid", "dashed")) +

  # adult data
  geom_jitter(
    data = variationBoxInd %>% filter(sample == "adults"), 
    aes(x = 6.5, y = mean, shape = datacollection), alpha = .15, width = .05, height = .01,  
  ) +

@@

  labs(x = "Age in years", y = "Proportion correct", col = "Age in years", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) + 
  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
  theme(legend.position="none")

@@

```{r reli_data}
reli <- testtrials %>% 
  filter(studytype == "reli" & (ageInYears < 6 | ageInYears == 18) & completedReli == TRUE)

@@

```{r intCon_hedge_kids}
hedge_intCon_kids <- hedge_intCon %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = as.factor(ageInYears)), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 5, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
  labs(x = "Even trials", y = "Odd trials")

@@

```{r intCon_box_kids}
box_intCon_kids <- box_intCon %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = as.factor(ageInYears)), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(breaks = seq(0, 1, 0.2)) +
  labs(x = "Even trials", y = "Odd trials")

@@

```{r retest_hedge_kids}
hedge_retest_kids <- hedge_retest %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = as.factor(ageInYears)), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 4, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
  labs(x = "Testday 1", y = "Testday 2")

@@

# summary
psych::describeBy(box_retest, box_retest$sample)
```
```{r retest_box_kids}
box_retest_kids <- box_retest %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = as.factor(ageInYears)), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Testday 1", y = "Testday 2")

>>>>

```{r vali_data}
vali <- testtrials %>% 
  filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18)) %>% 
  mutate(ageInYears = factor(ageInYears, levels = c("3", "4", "5", "18")))
```

@@

```{r variation_hedge_plot}
hedge_variation_plot <- ggplot() +
  # child data
  geom_smooth(
    data = variationHedgeInd %>% filter(sample == "kids"),  
    aes(x = ageInYearsExact, y = mean, group = datacollection, lty = datacollection), 
    method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey",
  ) +

  geom_point(
    data = variationHedgeInd %>% filter(sample == "kids"), 
    aes(x = ageInYearsExact, y = mean, col = ageInYears, shape = datacollection, alpha = datacollection)
  ) +

  geom_pointrange(
    data = variationHedge %>% filter(sample == "kids"), 
    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = ageInYears, shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
  ) +

  scale_shape_manual(values = c(16, 18)) + 
  scale_alpha_discrete(range = c(1, 0.4)) + 
  scale_linetype_manual(values = c("solid", "dashed")) +

  # adult data
  geom_jitter(
    data = variationHedgeInd %>% filter(sample == "adults"), 
    aes(x = 6.5, y = mean, col = ageInYears, shape = datacollection), alpha = 0.5, width = .05, height = .01,  
  ) +

@@

@@

  geom_point(
    data = variationBoxInd %>% filter(sample == "kids"), 
    aes(x = ageInYearsExact, y = mean, col = ageInYears, shape = datacollection, alpha = datacollection)
  ) +

  geom_pointrange(
    data = variationBox %>% filter(sample == "kids"), 
    aes(x = as.numeric(as.character(ageInYears))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = ageInYears, shape = datacollection, alpha = datacollection), size = 0.8, position=position_dodge(width = 0.1)
  ) +

  scale_shape_manual(values = c(16, 18)) + 
  scale_alpha_discrete(range = c(1, 0.4)) + 
  scale_linetype_manual(values = c("solid", "dashed")) +

  # adult data
  geom_jitter(
    data = variationBoxInd %>% filter(sample == "adults"), 
    aes(x = 6.5, y = mean, col = ageInYears, shape = datacollection), alpha = 0.5, width = .05, height = .01,  
  ) +

@@

  labs(x = "Age in years", y = "Proportion correct", col = "Age in years", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) + 
  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
  theme(legend.position="none")

@@

```{r reli_data}
reli <- testtrials %>% 
  filter(studytype == "reli" & (ageInYears < 6 | ageInYears == 18) & completedReli == TRUE) %>% 
  mutate(ageInYears = factor(ageInYears, levels = c("3", "4", "5", "18")))

@@

```{r intCon_hedge_kids}
hedge_intCon_kids <- hedge_intCon %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = ageInYears), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 5, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
  labs(x = "Even trials", y = "Odd trials")

@@

```{r intCon_box_kids}
box_intCon_kids <- box_intCon %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_even_trials, y = mean_odd_trials)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = ageInYears), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(breaks = seq(0, 1, 0.2)) +
  labs(x = "Even trials", y = "Odd trials")

@@

```{r retest_hedge_kids}
hedge_retest_kids <- hedge_retest %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = ageInYears), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 4, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
  labs(x = "Testday 1", y = "Testday 2")

@@

# summary
psych::describeBy(box_retest, box_retest$sample)
```
```{r retest_box_kids}
box_retest_kids <- box_retest %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = ageInYears), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Testday 1", y = "Testday 2")
